\documentclass[12pt]{article}
\usepackage{geometry} 
\usepackage{hyperref}
\geometry{letterpaper}
\geometry{margin=1in}

\begin{document}
\pagenumbering{arabic}

\linespread{1}

\title{Codebook}
\author{Coding raw\_user\_address errors in contacts-export20140617.csv}
\date{\today}

\maketitle

\paragraph{Incomplete information}
\begin{itemize}
\item 1 --- Ward only: only a ward number was entered (i.e. ``Ward 3'')
\item 2 --- Zip code only: only a zip code was entered (a four digit number)
\item 3 --- Street number only: only a street number was entered ($<$ than a four digit number)
\item 4 --- Zip code + other location info: a zip code was entered with other location information (i.e. a city or street name)
\item 5 --- Street number + other location info: a street number was entered with other location information (i.e. a city or street name), but is incomplete (e.g. 24 main street, 52 Pretoria)
\end{itemize}
\paragraph{Incorrect information}
\begin{itemize}
\item 11 --- Phone number: the user entered a phone number (a ten digit number)
\item 12 ---Random number: the user entered a number that could not be considered a phone number, zip code, or street number.
\item 13 --- Unrecognized address: the user submitted an address in the correct format with a street number and enough words to form a full address. However, the address was not recognized. This includes misspellings, unconventional abbreviations, and unofficial or fake addresses.
\item 14 --- P.O Box: only a P.O. Box was entered or a P.O. Box was entered instead of a street number. 
\item 15 --- Ward first: a ward number was entered first or ward was misspelled.
\end{itemize}
\paragraph{Extraneous information}
\begin{itemize}
\item 21 --- Party name: the user entered a party name or statement of support for a party
\item 22 --- Expletives: the user entered an expletive. 
\item 23 --- Single character: the user entered only a single letter or punctuation character. 
\item 24 --- Personal responses: the user entered a brief, random reply (hi, hello, thanks, a question, or a statement beginning in ``I'') 
\item 25 --- Other responses: the user entered a brief reply that could be interpreted as a response to other questions on the survey (yes, no, okay, back, exit, 1. Accept \& Join, $\ast$100\#) 
\end{itemize}


\end{document}
